### 2015-02-22 fundamentals/examples.tex
added single sentence paragraph to its neighbor
and -> among

Early progress has been promising. Many archetypes external to the \Cycamore library (Table \ref{tab:cycamore})
have been
\cite{huff_streamblender_2014,huff_commodconverter_2014}
or are being
\cite{flanagan_bright-lite_2014,skutnik_nuclear_2014,huff_mktdriveninst_2014} developed for contribution to the
\Cyclus ecosystem. These archetypes provide the first examples of
developer-contributed capabilities.  They add to the fundamental \Cycamore
archetypes by providing physics-based reactors, separations logic, fuel
fabrication processing, storage facilities, and expanded institutional paradigms.

@@

The existence and diversity of these contributed archetypes
illustrate the power and potential of the community-based development approach
that \Cyclus has taken.

@@

This section will discuss the creation and results of a few simple fuel cycle
simulations to help illustrate the flexibility of \Cyclus. These simulations
are designed to illustrate Cyclus' capability.  Many simplifying assumptions
have been made with respect to material compositions, fuel transmutation, and
others. The three fuel cycles examined are:

>>>>

Early progress has been promising. Many archetypes external to the \Cycamore
library (Table \ref{tab:cycamore}) have been
\cite{huff_streamblender_2014,huff_commodconverter_2014} or are being
\cite{flanagan_bright-lite_2014,skutnik_nuclear_2014,huff_mktdriveninst_2014}
developed for contribution to the \Cyclus ecosystem. These archetypes provide
the first examples of developer-contributed capabilities.  They add to the
fundamental \Cycamore archetypes by providing physics-based reactors,
separations logic, fuel fabrication processing, storage facilities, and expanded
institutional paradigms.  The existence and diversity of these contributed
archetypes illustrate the power and potential of the community-based development
approach that \Cyclus has taken.

@@

@@

This section will discuss the creation and results of a few simple fuel cycle
simulations to help illustrate the flexibility of \Cyclus. These simulations are
designed to illustrate Cyclus' capability.  Many simplifying assumptions have
been made with respect to material compositions, fuel transmutation, among
others. The three fuel cycles examined are:
